Discrete Quantum Theories and Computing

### 2019-02-27 dissertation.tex
dissertation.lyx Acknowledgments Updates...

\item Other friends, including Shu-Ling Wang (王舒齡), Wan-Ling ``Wynnie''
Chang (張婉鈴), Yu-Jung Lin (林宇容), Winnie Lou (何慧芳), Yi-Rong Yang (楊宜蓉),
Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
Gong (龔治齊), and 江靜宜, \ldots , etc.

>>>>

\item Other friends, including Shu-Ling Wang (王舒齡), Wan-Ling ``Wynnie''
Chang (張婉鈴), Yu-Jung Lin (林宇容), Winnie Lou (何慧芳), Yi-Rong Yang (楊宜蓉),
Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
Gong (龔治齊), 江靜宜, and the office of International Services\ldots ,
etc.
